%-------------------------
% Resume in Latex
% Author : Vinay Padma
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingWithSummary}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & #2 \\
      \multicolumn{2}{p{0.97\textwidth}}{\textit{\small #3}} \\
      \textit{\small\textbf{#4}} & \textit{\small #5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & #2 \\
      \textit{\small\textbf{#3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeRoleSubHeading}[2]{
    \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small\textbf{#1}} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Vinay Padma} \\ \vspace{1pt}
    \small +1 415 579 6769 $|$ \href{mailto:vinay.padma@gmail.com}{\underline{vinay.padma@gmail.com}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {University of Waterloo}{Waterloo, ON}
      {Bachelor of Applied Science in Electrical Engineering, Honors}{2012 -- 2017}
    \educationSubheading
      {Turner Fenton Secondary School}{Brampton, ON}
      {International Baccalaureate Diploma}{2008 -- 2012}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, C++11, C, Python 3, SQL, MATLAB} \\
     \textbf{Technologies}{: AWS (EC2, KMS, S3, IoT), Temporal Workflow, Kafka, MongoDB, Elasticsearch, Redis, gRPC, Protobuf} \\
     \textbf{Core competencies}{: Large-scale distributed systems design, API design, Systems \& embedded programming, Android} \\
     \textbf{Software Tools}{: Git, Vim, Perforce, Android Studio, Prometheus, Splunk, SignalFx, Pagerduty}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheadingWithSummary
      {Stripe, San Francisco / New York}{2018 -- Present}
      {Founding engineer for Stripe Terminal, the company’s in-person payment product, launched in 2018. Acted as domain expert and API reviewer; supported scaling of product and team to 70+ engineers (100+ with hardware). Terminal now processes \$80B+ annually. Select major projects are listed below.}
      {Engineering, Terminal Core Infrastructure}{Aug 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Designed and scaled OTA deployment infrastructure for client software across 1M+ devices with enterprise-grade features (gradual rollout, observability, MDM functionality). Multiple patents granted.}
        \resumeItem{Built a platform for users to upload and deploy custom apps on field devices; contributed to signing, API design, and web dashboards. As of 2025, 140k+ devices use this, processing \$9.5B in incremental transactions.}
        \resumeItem{Implemented dynamic TLS certificate provisioning for local HTTPS servers on devices via Let's Encrypt; issued 100M+ certs, enabling \$100B+ in transactions.}
        \resumeItem{Developed a data pipeline using CDC to populate Elasticsearch for search and analytics; powers dashboards and enterprise features with rich query capability.}
      \resumeItemListEnd
    \resumeRoleSubHeading
      {Engineering, Terminal Device Platform}{Mar 2018 -- Aug 2020}
      \resumeItemListStart
        \resumeItem{Built C++ embedded applications for Terminal payment devices, implementing payments, HTTPS server, networking, and threading model.}
        \resumeItem{Ported embedded apps to Android (Kotlin) to support new hardware and scale development team. Launched Stripe’s first Android-based Terminal device in 2020.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Index, San Francisco (Acquired by Stripe)}{2017 -- 2018}
      {Member of Technical Staff, Platform \& Embedded Technologies}{}
      \resumeItemListStart
        \resumeItem{Contributed to core embedded and platform technologies, laying groundwork before the Stripe acquisition}
      \resumeItemListEnd

    \resumeSubheadingWithSummary
      {Apple Inc, Cupertino, CA}{2015 -- 2016}
      {Designed and built systems to test various RF systems, such as the antenna on the iPhone X through 2 internships.}
      {RF Instrumentation Software Engineering Intern}{2016}
    \resumeRoleSubHeading
      {Wireless/RF Engineering Intern}{2015}    
    
    \vspace{2pt}

    \resumeSubheading
      {Sandvine Inc, Waterloo, ON}{2015}
      {Embedded Software Engineering Intern}{}
      \resumeItemListStart
        \resumeItem{Embedded C++ development: designed a multi-constraint traffic load-balancing system. Patent granted}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PATENTS-----------
\section{Patents}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://patents.google.com/patent/US20240201975A1/en}{\underline{Stripe, US20240201975A1}}, Deploying assets}}{Pending, 2024}
      \resumeProjectHeading
          {\textbf{\href{https://patents.google.com/patent/US20240152899A1/en}{\underline{Stripe, US20240152899A1}}, Handoff between applications on a payment terminal}}{Pending, 2024}
      \resumeProjectHeading
          {\textbf{\href{https://patents.google.com/patent/US20240152394A1/en}{\underline{Stripe, US20240152394A1}}, Deploying applications to a payment terminal}}{Pending, 2024}
      \resumeProjectHeading
          {\textbf{\href{https://patents.google.com/patent/US20240152653A1/en}{\underline{Stripe, US20240152653A1}}, Secure signing of applications for a payment terminal}}{Pending, 2024}
      \resumeProjectHeading
          {\textbf{\href{https://patents.google.com/patent/US20170264550A1/en?oq=US2017264550}{\underline{Sandvine, US20170264550A1}}, System and method for packet distribution on a network}}{Granted, 2017}
    \resumeSubHeadingListEnd

\end{document}
